---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# r.proxy

<!-- badges: start -->
<!-- badges: end -->

The goal of r.proxy is to Set Proxy in R Console.

This project is inspired by [zsh-proxy](https://github.com/SukkaW/zsh-proxy).

## Installation

You can install the development version of r.proxy like so:

``` r
# install.packages("devtools")
devtools::install_github("xiayh17/r.proxy")
```

## Example

This is a basic example which shows you how to use it:

Start proxy by `proxy()`

Configrations interactive will show only in the first time you use. 

```{r start_first, eval=FALSE}
r.proxy::proxy()
```

``` r
#> This maybe the first time proxy4you be load. 
#> Please complete below configrations:)
#> Default setting can be accessed by Enter with nothing
#> [socks5 proxy] {Default as 127.0.0.1:7890} (address:port): 192.168.3.15:7890
#> [https proxy] {Default as 127.0.0.1:7890} (address:port): 
#> [http proxy] {Default as 127.0.0.1:7890} (address:port): 
#> Your setting have been save in ~/.Rproxy
#> Proxy info: 
#> http://127.0.0.1:7890http://192.168.3.15:7890socks5://127.0.0.1:7890
#> check what your ip is: 
#> IPv4: 
#> 91.243.81.71
#> 
#> Details: 
#> {
#>     "organization": "MoreneHost",
#>     "longitude": 6.1661,
#>     "timezone": "Europe/Luxembourg",
#>     "isp": "MoreneHost",
#>     "offset": 3600,
#>     "asn": 199524,
#>     "asn_organization": "G-Core Labs S.A.",
#>     "country": "Luxembourg",
#>     "ip": "91.243.81.71",
#>     "latitude": 49.7498,
#>     "continent_code": "EU",
#>     "country_code": "LU"
#> }
```

```{r start_after, eval=FALSE}
r.proxy::proxy()
```

``` r
#> Proxy info: 
#> http://127.0.0.1:7890http://192.168.3.15:7890socks5://127.0.0.1:7890
#> check what your ip is: 
#> IPv4: 
#> 91.243.81.71
#> 
#> Details: 
#> {
#>     "organization": "MoreneHost",
#>     "longitude": 6.1661,
#>     "timezone": "Europe/Luxembourg",
#>     "isp": "MoreneHost",
#>     "offset": 3600,
#>     "asn": 199524,
#>     "asn_organization": "G-Core Labs S.A.",
#>     "country": "Luxembourg",
#>     "ip": "91.243.81.71",
#>     "latitude": 49.7498,
#>     "continent_code": "EU",
#>     "country_code": "LU"
#> }
```

Stop proxy by `noproxy()`

```{r stop}
r.proxy::noproxy()
```

Reset proxy by `init_proxy()`

```{r reset, eval=FALSE}
r.proxy::init_proxy()
```

``` r
#> This maybe the first time proxy4you be load. 
#> Please complete below configrations:)
#> Default setting can be accessed by Enter with nothing
#> [socks5 proxy] {Default as 127.0.0.1:7890} (address:port): 192.168.3.15:7890
#> [https proxy] {Default as 127.0.0.1:7890} (address:port): 
#> [http proxy] {Default as 127.0.0.1:7890} (address:port): 
#> Your setting have been save in ~/.Rproxy
```

Check your IP

```{r check}
r.proxy::check_ip()
```

Test your connect

[speedtest](https://github.com/hrbrmstr/speedtest) will be used in this step

```{r test}
speedtest::spd_test()
r.proxy::proxy()
speedtest::spd_test()
r.proxy::noproxy()
```
